
---
title: "Analysing Zomato Dataset Using R"
author: "Hariprashath R"
date: "`r Sys.Date()`"
output: html_document
---

## Setting up the Environment
Notes: Setting up the R environment by loading the 'tidyverse' package and other packages also. 
```{r loading packages}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr)
library(tibble)
library(purrr)
library(stringr)
library(readxl)
```

# Load the dataset
 The dataset used in this project was downloaded from Kaggle: <https://www.kaggle.com/datasets/bharathdevanaboina/zomato-restaurants-dataset>
 changing the file type: csv to excel file.
 
```{r}
z <- read_excel("F:/Portfolia_Projects/Project_3/zomato_dataset_1.xlsx")
dim(z)
summary(z)
```

# Top 12 Restaurant by Branches Registred

 
```{r fig.width=8, fig.height=6}
g <- z %>% 
        select(Restaurant_Name) %>% 
        group_by(Restaurant_Name) %>%
        summarise(count = n()) %>% 
        arrange(desc(count)) %>%  
        slice(1:12)

ggplot(g, aes(x=reorder(Restaurant_Name, -count), y=count)) +
    geom_bar(stat = "identity", fill="steelblue", color = "red") +    
    geom_text(size=3, aes(label=count),vjust = -0.5)+
    scale_x_discrete(labels = function(x) stringr :: str_wrap(x,width = 6))+
    labs(x = "Restaurant_Name", y = "Restaurant Branches", title="Top 12 Registerend Restaurants and Branches")+    
    theme(plot.title = element_text(hjust=0.5),legend.position = "none",        
          axis.text  = element_text(size = 8))
```


### Analyse :
       From the Analysis, McDonald's has registered the more branches with **2059 Restaurants**.
       Fast food Restaurants has registered the more branches with our company.
       
# Top 12 Restaurant by Dining Votes

```{r plot_wider, fig.width=10, fig.height=6}
c <- z %>% 
      group_by(Restaurant_Name) %>%
      summarise(count = sum(`Dining Votes`)) %>% 
      arrange(desc(count)) %>%  
      slice(1:12)
    
ggplot(c, aes(x = reorder(Restaurant_Name, -count), y=count,fill = Restaurant_Name)) +    
    geom_col()+
    labs(x="Restaurant_Name", y="Total Dining Votes", title = "Top 12 Restaurants with the Highest Dining Votes")+
    geom_text(size=3,aes(label=count),vjust = -0.5)+
    scale_y_continuous(labels = scales::comma)+
    scale_x_discrete(labels = function(x) stringr :: str_wrap(x,width = 6))+
    theme(plot.title = element_text(hjust=0.5),legend.position = "none",
          axis.text = element_text(size = 8))

```



###### Analyse :
       Fast food restaurants had received more dining votes as well as sweets shops. 
       Kanha Restaurant has received highest number of votes with**8,14,448 votes** from the customers.  
 
# Top 12 Bestselling Food items with Bestseller

```{r plot-wider, fig.width=7, fig.height=6}
i <- z %>% 
        filter(Best_Seller == "BESTSELLER") %>%            
        group_by(Item_Name) %>% 
        summarize(Total_Votes = sum(Votes)) %>% 
        arrange(desc(Total_Votes)) %>% 
        slice(1:12)
    
ggplot(i, aes(x = reorder(Item_Name, Total_Votes), y = Total_Votes)) +
    geom_bar(stat = "identity", color = "steelblue", size=1)+
    coord_flip()+
    theme_light()+
    labs(x="Bestselling Food Items", y="Total Votes", title = "Top 12 Bestselling Food Items")+
    geom_text(size=3,aes(label = Total_Votes),vjust = 0.5, hjust= -0.2)+
    scale_y_continuous(labels = scales::comma)+
    scale_x_discrete(labels = function(y) stringr :: str_wrap(y,width = 6))+
    ylim(0,80000)+
    theme(plot.title = element_text(hjust=0.5),legend.position = "none",
          axis.text = element_text(size = 8))
    
```



###### Analyse : 
      As per the visual, **Chicken Biryani** has sold more compared to other food items. Also, Non-vegetarian dishes 
      has sold more when compared to the vegetarian dishes. Prefer: More Non-vegetarian foods 
      rather than vegetarian foods.  

# City Based on the Average Prices

```{r fig.width=8, fig.height=4}
l <- z %>% 
        group_by(City) %>% 
        summarise(Avg_Price = mean(Prices)) %>% 
        arrange(desc(Avg_Price)) %>%
        slice(1:12)

ggplot(l, aes(City,Avg_Price))+
    geom_point(size = 2)+
    geom_line(color="red")+
    scale_y_continuous(limits = c(0, 700))+
    scale_x_discrete(labels = function(x) stringr :: str_wrap(x,width = 6))+
    labs(title = "City based on the Average_Price")+
    theme(plot.title = element_text(hjust=0.5))
```



###### Analyse :
        From that, Ulsoor city had registered the highest Avg_Price. But, mostly other cities had  
        Avg_Price between 200 to 400.
        
# Correlation b/w Dining_Rating and Delivery_Rating

```{r}
w <-  z %>% 
      drop_na() %>% 
      filter(Dining_Rating > 3.0 & Delivery_Rating > 3.5)
    
ggplot(w, aes(Dining_Rating, Delivery_Rating))+
    geom_tile(fill = "steelblue")+
    labs(title = "Correlation between Dining and Delivery Rating")+
    theme(plot.title = element_text(hjust=0.5),legend.position = "none")+
    scale_y_continuous(limits = c(3.5,4.6),
                       breaks = c(3.0,3.2,3.4,3.6,3.8,4.0,4.2,4.4,4.6))
  
```



###### Analyse :
        From the plot graph, Dining_Rating had rated between 3.5 to 4.5 and 
        Delivery_Rating had rated between 3.6 to 4.4.
        From that Ratings  are good.